Group 5 Report

### 2022-07-31 Report/Draft Dashboard section.Rmd
Experimenting with output options.

---
title: "Dashboard section"
author: "Torbjørn Skinnemoen Ottersen"
date: '2022-07-23'
output:
  pdf_document:
    highlight: pygments
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

@@

- More elegant to use lines (***) around the code blocks and one of the non-default syntax highlight styles, I think. (See first two blocks for example.)

@@

As the dashboard uses a fair number of packages, it uses the pacman package to ensure they are installed:

***
```{r dashboard_packages, eval=FALSE}
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools
)
```
***

@@

***
```{r dashboard_sidebar, eval=FALSE}
# HTML upload
fileInput("html", label = "Upload html file", accept = ".html")

@@

# Button
actionButton("click", "Analyse")
```
***

@@

If the validation is successful the files are read using the functions developed for this purpose, which conduct further testing, outputting error messages using `validate()`:
```{r dashboard_file_functions, eval=FALSE}
# Data reading functions =======================================================

>>>>

---
title: "Dashboard section"
author: "Torbjørn Skinnemoen Ottersen"
date: '2022-07-23'
output:
  pdf_document:
    highlight: pygments
  html_document:
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
line <- "***"
```

@@

- More elegant to use lines (***) around the code blocks and one of the non-default syntax highlight styles, I think. (See first two blocks for example.) (If output is supposed to be pdf.)

@@

As the dashboard uses a fair number of packages, it uses the pacman package to ensure they are installed, to avoid the user being confronted with messages about missing packages:

<!--# Might need to include tinytex? Or is that overkill? -- if (!require("tinytex") install.packages("tinytex"); tinytex::install_tinytex())-->

`r if (knitr::is_latex_output()) {line}`

```{r dashboard_packages, eval=FALSE}
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools
)
```

`r if (knitr::is_latex_output()) {line}`

@@

`r if (knitr::is_latex_output()) {line}`
```{r dashboard_sidebar, eval=FALSE}
# HTML upload
fileInput("html", label = "Upload html file", accept = ".html")

@@

# Button
actionButton("click", "Analyse")
```

`r if (knitr::is_latex_output()) {line}`

@@

If the validation is successful the files are read using the functions developed for this purpose, which conduct further testing, outputting error messages using `validate()`:
```{r dashboard_file_functions, eval=FALSE, class.source = "fold-hide"}
# Data reading functions =======================================================

### 2022-07-31 Report/report figure size testing.Rmd
Experimenting with output options.

---
title: "Group 5 Report"
author: "ISSSV1337 Group 5"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

@@

<!--# Inkluderer spoilers, kan man si, hvis man vil finne ut av hvordan man styrer bildestørrelse o.l. selv. -->

@@

>>>>

---
title: "Group 5 Report"
author: "ISSSV1337 Group 5"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

@@

<!--# Inkluderer spoilers, kan man si, hvis man vil finne ut av hvordan man styrer billedstørrelse o.l. selv. -->

@@

```{r, out.width="45%", fig.cap="The dashboard", fig.show='hold', fig.align='center'}
knitr::include_graphics("Images/Dashboard_page_1.png")
knitr::include_graphics("Images/Dashboard_page_2.png")
```

```{r, out.width="50%", fig.align='center', fig.cap="Sample dashboard report"}
knitr::include_graphics("Images/Dashboard_report.png")
```
